---
title: "Hypergraphs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Hypergraphs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 9,
                      fig.height = 7, out.width = "100%")
has_igraph <- requireNamespace("igraph", quietly = TRUE)
join_and <- function(v) sub(", ([^,]*)$", " and \\1", toString(v))
n_steps <- length(unique(hypergraphs::tutoring_events$step))
```

Higher-order network models extend pairwise networks in two directions. One
represents interactions among groups of nodes with hypergraphs and simplicial
complexes; the other represents memory in paths. This document covers
hypergraphs. A hypergraph consists of a set of nodes and a set of
hyperedges, and a hyperedge is a subset of the nodes of any size. An edge of
a network is the special case of a hyperedge with two nodes. A hypergraph is
represented by its incidence matrix, which has one row per node, one column
per hyperedge, and an entry of one where the node belongs to the hyperedge.
The projection of a hypergraph to a network replaces each hyperedge by the
pairs of its nodes, and different hypergraphs can have the same projection.
Measures computed from the incidence matrix keep the information that the
projection loses.

## Data

The examples use `tutoring_events`, a data frame in long format with one row
per event, from `r format(n_steps, big.mark = ",")` problem steps that
learners worked through with an AI tutor. A step begins with the task, the
learner attempts an answer, and the answer is correct or incorrect. After an
incorrect answer the tutor responds with guidance, a question, an order, a
refutation, a prompt to reflect or comfort, and the learner reattempts or
gives up. A step ends with `Completed` after a correct answer and with
`Stopped` when it ends without one. A trial is the part of a step between two
answers.

```{r data}
library(hypergraphs)
head(tutoring_events, 12)
```

```{r data-values, include = FALSE}
n_trials <- length(unique(tutoring_events$trial))
n_events <- length(unique(tutoring_events$event))
```

The data contain `r format(n_trials, big.mark = ",")` trials and
`r n_events` distinct events.

## Hypergraphs from observed groups

When group membership is observed, each group is a hyperedge. In an event
log, the events of a session form such a group, and a trial is a session in
this sense. In `hypergraph()`, `action` names the column of the events and
`session` the column of the trials, and the events of each trial become one
hyperedge.

```{r trials}
trial_hg <- hypergraph(tutoring_events, action = "event", session = "trial")
trial_hg
```

```{r trials-values, include = FALSE}
trial_edges <- hg_get(trial_hg)
size_counts <- table(trial_edges$size)
modal_size <- names(size_counts)[which.max(size_counts)]
n_sets <- length(unique(trial_edges$members))
```

Most trials contain `r modal_size` events, and the largest contain
`r max(trial_edges$size)`. Many trials contain the same events: the
`r format(n_trials, big.mark = ",")` trials hold `r n_sets` distinct sets.
A hypergraph whose hyperedges repeat is plotted as its distinct sets.

```{r trials-plot, fig.width = 10, fig.height = 9}
plot(trial_hg)
```

Each set is plotted as a hull coloured by its number of trials, and each
event as a circle whose area is the number of trials that contain it. Most
of the sets are rare and overlap the frequent ones. The minimum support of
frequent-set mining keeps the sets that occur in at least a given share of
the trials. With `min_share = 0.01`, the sets of at least 1% of the trials
are kept.

```{r common-trials}
common_trials <- hypergraph(tutoring_events, action = "event",
                            session = "trial", min_share = 0.01)
common_trials
```

```{r common-trials-values, include = FALSE}
common_cover <- round(100 * sum(hg_get(common_trials, what = "sets")$share))
```

```{r common-trials-plot, fig.width = 10, fig.height = 9}
plot(common_trials)
```

The `r common_trials$n_hyperedges` sets cover `r common_cover`% of the
trials. The sets of a stopped step, with `Comfort`, `GiveUp` and `Stopped`,
lie apart from the sets of the first trial and the reattempts.

The degree of an event is the number of hyperedges that contain it.

```{r trial-nodes}
trial_nodes <- hg_get(trial_hg, what = "nodes", sort_by = "degree")
trial_nodes
```

## Frequent sets

Most trials fall into a few of the `r n_sets` sets.
Counting the sets and keeping the most frequent ones as hyperedges
summarises the data by its common combinations. With `top = 8`, the eight
most frequent sets are kept.

```{r sets}
trial_sets <- hypergraph(tutoring_events, action = "event",
                         session = "trial", top = 8)
trial_set_table <- hg_get(trial_sets, what = "sets")
trial_set_table
```

```{r sets-values, include = FALSE}
top_share <- round(100 * sum(trial_set_table$share))
```

The eight sets account for `r top_share`% of the trials. The most frequent
set, `r trial_set_table$set[1]`, is a step completed on its first trial. The
next are a first trial with an incorrect answer, a correct first trial that
opens with `Begin`, and reattempts after guidance or a question, which are
correct or incorrect.

```{r sets-plot, fig.width = 10, fig.height = 7}
plot(trial_sets)
```

With `group`, the sets are counted separately within each value of a
comparison variable. The `outcome` column records whether a step is
completed with a correct answer or stopped without one.

```{r sets-by}
outcome_sets <- hypergraph(tutoring_events, action = "event",
                         session = "trial", group = "outcome", top = 6)
outcome_set_table <- hg_get(outcome_sets, what = "sets")
outcome_set_table
```

```{r sets-completed-plot, fig.width = 9, fig.height = 7}
plot(outcome_sets, group = "completed")
```

```{r sets-stopped-plot, fig.width = 9, fig.height = 7}
plot(outcome_sets, group = "stopped")
```

The frequent trials of completed steps are correct first trials, incorrect
first trials and correct reattempts after guidance or a question. The
frequent trials of stopped steps are incorrect first trials and incorrect
reattempts after a question, guidance or an order. In the set
`Comfort + GiveUp + Stopped` the tutor comforts the learner, the learner
gives up and the step ends without a correct answer.

## Hypergraphs from sequences

When only the order of events is recorded, hyperedges are formed from windows
of consecutive events in the sequence of events of each step. Each window of
`window` events is reduced to the set of its distinct events, and identical
sets are merged into one hyperedge whose weight is the number of windows that
produced it. The argument `action` names the column of the events, `actor`
the column of the steps and `time` the column that orders the events.

```{r window}
window_hg <- hypergraph(tutoring_events, action = "event", actor = "step",
                        time = "position", window = 3)
window_hg
window_edges <- hg_get(window_hg, sort_by = "weight", top = 8)
window_edges
```

```{r window-plot, fig.width = 10, fig.height = 9}
plot(window_hg)
```

```{r window-values, include = FALSE}
n_windows <- sum(hg_get(window_hg)$weight)
```

The `r format(n_windows, big.mark = ",")` windows give
`r window_hg$n_hyperedges` distinct hyperedges. A window with a repeated
event contains fewer distinct events than its length, so some hyperedges
have two nodes or one. With `min_weight`, only hyperedges produced by at
least that many windows are kept, and `hg_subset()` with `size = 3` keeps
the windows of three distinct events and drops the events left in none.

```{r window-frequent}
frequent_windows <- hypergraph(tutoring_events, action = "event",
                               actor = "step", time = "position",
                               window = 3, min_weight = 2000)
frequent_windows <- hg_subset(frequent_windows, size = 3)
frequent_windows
```

```{r window-frequent-plot, fig.width = 8, fig.height = 7}
plot(frequent_windows)
```

Each hull is a window of three events, coloured by the number of windows
that contain exactly these events. Windows span the boundaries between
trials, and the window length is set by the analyst. The remaining sections
use the trials, which the data record.

## Projection to a network

The projection of a hypergraph is the network in which two nodes are joined
when they belong to a common hyperedge, with a weight equal to the number of
such hyperedges.

```{r project}
trial_network <- pairwise_network(trial_hg)
trial_network_edges <- hg_get(trial_network, sort_by = "weight", top = 8)
trial_network_edges
```

```{r project-plot, fig.width = 7, fig.height = 7}
plot(trial_network)
```

```{r project-values-pre, include = FALSE}
n_pairs <- nrow(hg_get(trial_network))
```

Each edge joins two events with a width that grows with the number of trials
that contain both. The widest edges join `Task`, `Attempt`, `Correct` and
`Completed`, which occur together in most first trials, and the edges of
`Comfort`, `GiveUp` and `Stopped` are thin. The network records how often two
events
occur in the same trial and leaves out which other events occur with them.

A hypergraph can also be inferred from a network by taking every clique, a
set of nodes that are all joined to each other, as a hyperedge. With
`include_pairwise = FALSE` the cliques of three or more nodes are kept, and
`max_size` is the size of the largest clique kept, here the size of the
largest trial.

```{r project-back}
clique_hg <- hypergraph(trial_network, max_size = 6, include_pairwise = FALSE)
clique_hg
```

```{r project-back-plot, fig.width = 9, fig.height = 8}
plot(clique_hg)
```

```{r project-values, include = FALSE}
as_keys <- function(members) {
  vapply(strsplit(members, ", ", fixed = TRUE),
         \(m) paste(sort(m), collapse = " + "), character(1))
}
observed_keys <- as_keys(unique(hg_get(trial_hg)$members))
observed_keys <- observed_keys[lengths(strsplit(observed_keys, " + ",
                                                fixed = TRUE)) >= 3]
inferred_keys <- as_keys(hg_get(clique_hg)$members)
n_true <- sum(inferred_keys %in% observed_keys)
n_found <- sum(observed_keys %in% inferred_keys)
```

The network has `r n_pairs` pairs, and its cliques of three to
`r max(hg_get(clique_hg)$size)` events give `r clique_hg$n_hyperedges`
hyperedges. The trials contain `r length(observed_keys)` distinct sets of
three or more events, and `r n_found` of them are among the cliques. The
other `r clique_hg$n_hyperedges - n_true` cliques are sets whose pairs each
occur in some trial while the whole set occurs in none. Identifying the
observed groups among the cliques requires the hypergraph. The cliques cover
the events so densely that their hulls hide one another in the plot.

## Node measures

Node measures of a hypergraph are computed from its incidence matrix. The
hyperdegree of a node is the number of hyperedges that contain it, its
strength is the sum of the sizes of those hyperedges, and its number of
neighbours is the number of other nodes that share a hyperedge with it.

```{r measures}
node_measures <- hg_measures(trial_hg)
node_measures
trial_summary <- hg_measures(trial_hg, what = "summary")
trial_summary
```

```{r measures-values, include = FALSE}
participation <- subset(trial_summary,
                        measure == "pairwise_participation")$value
attempt_row <- subset(node_measures, node == "Attempt")
```

`Attempt` belongs to the first trial of every step, `Task` to that trial and
to some reattempts, and `Correct` and `Completed` to the trial that ends
every completed step, so these events have the highest hyperdegree.
Hyperdegree and the number of neighbours describe different aspects of
position. `Attempt` belongs to
`r format(attempt_row$hyperdegree, big.mark = ",")` trials and shares them
with `r attempt_row$n_neighbors` other events, and `Task` shares a trial with
every other event. The pairwise participation is the share of pairs of nodes
that belong to at least one common hyperedge. It is
`r sprintf("%.2f", participation)`, so
`r round(100 * (1 - participation))`% of the pairs of events never occur in
the same trial.

## Centrality

An eigenvector centrality gives a node a score that depends on the scores of
the nodes it shares hyperedges with. The clique centrality is the
eigenvector centrality of the projection. The Z and H centralities score a
node by the product of the scores of the other members of each of its
hyperedges. In the H centrality the score of the node itself is raised to the
power k - 1, where k is the size of the largest hyperedge, and the scores are
more even.

```{r centrality}
event_centrality <- hg_centrality(trial_hg, sort_by = "H")
event_centrality
```

The clique centrality is highest for the events of a correct first trial,
`Task`, `Attempt`, `Correct` and `Completed`, which occur together in most
steps. The Z and H centralities rank `Incorrect` third. An incorrect first
trial contains `Incorrect` with `Task` and `Attempt`, the two
highest-scoring events, and the product of their scores raises the score of
`Incorrect`.

PageRank on a hypergraph is the stationary distribution of a random walk that
moves from a node to a hyperedge that contains it and from the hyperedge to
one of its members, with a fixed probability of restarting at a random node.

```{r pagerank}
event_pagerank <- hg_pagerank(trial_hg, sort_by = "pagerank")
event_pagerank
```

`Comfort`, `GiveUp` and `Stopped` occur mostly together in the last trial of
a stopped step, so a walk that reaches one of them moves among the three for
several moves before it leaves. They rank seventh to ninth by PageRank and
close to zero by the clique and Z centralities.

## Communities and clusters

A community is a set of nodes that share more hyperedges with each other
than with the rest of the hypergraph. The communities of the events are
found with the map equation from 20 random starts, and the partition
reported is the medoid, the partition that agrees most with the other 19.

```{r communities, eval = has_igraph}
event_communities <- hg_communities(trial_hg, n_runs = 20, seeds = 1:20)
event_communities
```

Spectral clustering divides the nodes into `k` clusters by the eigenvectors
of the hypergraph Laplacian. Its final k-means step starts from random
centres, which `seed` fixes.

```{r cluster}
event_clusters <- hg_cluster(trial_hg, k = 3, seed = 1)
event_clusters
```

```{r cluster-values, include = FALSE}
members_of <- function(event) {
  label <- subset(event_clusters, node == event)$cluster
  join_and(subset(event_clusters, cluster == label)$node)
}
```

The clusters are the end of a stopped step (`r members_of("Stopped")`), the
events of a correct first trial (`r members_of("Completed")`), and the
incorrect answers, the reattempts and the moves of the tutor
(`r members_of("Guidance")`). The adjusted Rand index measures the agreement
between two partitions of the same nodes, corrected for chance.

```{r agreement, eval = has_igraph}
partition_agreement <- hg_agreement(event_communities, event_clusters)
partition_agreement
partition_table <- hg_agreement(event_communities, event_clusters,
                                what = "table")
partition_table
```

The map equation separates the end of a stopped step from the other events.
Spectral clustering divides the other events into those of a correct first
trial and those of the reattempts. The adjusted Rand index between the two
partitions is `r sprintf("%.2f", partition_agreement$ari)`.

## Null models

A structural pattern is assessed against random hypergraphs that keep the
size of every hyperedge and the degree of every node. Such hypergraphs are
generated by repeated swaps of members between pairs of hyperedges, and the
observed value of a statistic is compared with its distribution over the
random hypergraphs. The comparison is made on the trials of the stopped
steps.

```{r null}
stopped_events <- subset(tutoring_events, outcome == "stopped")
stopped_hg <- hypergraph(stopped_events, action = "event", session = "trial")
plot(stopped_hg)
stopped_null <- hg_null_test(stopped_hg, n = 99, seed = 1,
                          statistic = c("pairwise_participation",
                                        "avg_jaccard", "repeated_edges"))
stopped_null
```

```{r null-values, include = FALSE}
null_row <- function(s) subset(stopped_null, statistic == s)
pp <- null_row("pairwise_participation")
re <- null_row("repeated_edges")
aj <- null_row("avg_jaccard")
```

In the random hypergraphs `r sprintf("%.1f", 100 * pp$null_mean)`% of the
pairs of events occur together in some trial, against
`r round(100 * pp$observed)`% in the data. About
`r format(round(re$null_mean), big.mark = ",")` trials repeat the set of an
earlier trial, against `r format(re$observed, big.mark = ",")` in the data,
and the mean Jaccard index between two trials is `r round(aj$null_mean, 2)`,
against `r round(aj$observed, 2)`. The trials of stopped steps repeat a
small number of sets, and each set keeps together events that the random
hypergraphs spread over many trials. The p-value of `r pp$p_value` is the
smallest attainable with 99 random hypergraphs. The observed pairwise
participation lies `r round(abs(pp$z))` standard deviations below the mean of
the random hypergraphs, and the number of repeated trials
`r round(abs(re$z))` standard deviations above it.

## Other higher-order structures

A corpus of documents forms a hypergraph in which each document is a
hyperedge over its words, built with `text_hypergraph()`. Memory networks
are estimated from paths with `hon()`, and simplicial complexes, in which
every subset of a relation is also a relation, are built with
`simplicial()`. The help page `?hypergraphs` lists the functions of each
family.
