---
title: "Analysis of ICSID tribunals in claims against Argentina"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis of ICSID tribunals in claims against Argentina}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE,
                      fig.width = 8, fig.height = 5, out.width = "100%",
                      dpi = 150)
library(hypergraphs)
comma <- function(x) format(x, big.mark = ",", trim = TRUE)
pct <- function(x) sprintf("%.0f%%", 100 * x)
num <- function(x, d = 2) sprintf(paste0("%.", d, "f"), x)
day <- function(x) trimws(format(x, "%e %B %Y"))
```

```{r ranking, include = FALSE}
case_states <- unique(subset(icsid_tribunals, select = c(case, respondent)))
claims <- aggregate(case ~ respondent, data = case_states, FUN = length)
argentina_claims <- subset(claims, respondent == "Argentine Republic")$case
argentina_rank <- sum(claims$case > argentina_claims) + 1L
rank_word <- switch(argentina_rank, "largest", "second-largest",
                    "third-largest")
```

Of the `r comma(nrow(case_states))` cases of the International Centre for
Settlement of Investment Disputes (ICSID) in the `icsid_tribunals` data,
`r argentina_claims` were brought against the Argentine
Republic, the `r rank_word` number against any state. Each case is heard by
a tribunal of three arbitrators, and the tribunals of the claims against one
state form a temporal hypergraph. Its nodes are the arbitrators, its
hyperedges the tribunals, and each hyperedge is active from the
constitution of the tribunal to the conclusion of its case. A hypergraph
keeps the tribunal as a unit, where a network of pairs of arbitrators
dissolves it into three ties, and its temporal form keeps apart tribunals
that never sat at the same time. This document asks three questions of the
tribunals in the claims against Argentina. The first is who decided the
claims, and how concentrated the seats were. The second is whether the same
panels sat again more often than the numbers of tribunals of the
arbitrators imply. The third is how the structure of the docket changed
over two decades, and which tribunals connected it at each time. The
tribunals are analysed over time and compared with the other ICSID cases.

## Data

The cases against Argentina are the rows of `icsid_tribunals` with
Argentina as the respondent, one row per seat on a tribunal.

```{r data}
argentina <- subset(icsid_tribunals, respondent == "Argentine Republic")
```

```{r data-values, include = FALSE}
n_cases <- length(unique(argentina$case))
n_arbitrators <- length(unique(argentina$arbitrator))
n_pending <- length(unique(subset(argentina, !is_concluded)$case))
case_dates <- unique(subset(argentina, select = c(case, constituted)))
origin_date <- min(case_dates$constituted)
end_offset <- as.numeric(as.Date("2023-06-15") - origin_date)
first_tribunal <- format(origin_date, "%Y")
last_tribunal <- format(max(case_dates$constituted), "%Y")
early <- nrow(subset(case_dates, constituted < as.Date("2006-01-01")))
wave <- nrow(subset(case_dates, constituted >= as.Date("2003-01-01") &
                      constituted < as.Date("2005-01-01")))
dated_pending <- unique(subset(argentina, !is_concluded & !is.na(concluded),
                               select = c(case, concluded)))
year_of <- function(t) format(origin_date + t, "%Y")
```

The `r n_cases` cases were heard by `r n_arbitrators` arbitrators. Their
tribunals were constituted between `r first_tribunal` and
`r last_tribunal`, `r early` of them before 2006 and `r wave` in 2003 and
2004 alone. `r n_pending` cases are marked as pending on 15 June 2023, the
end of observation. One of these, `r dated_pending$case`, also carries a
conclusion date, `r day(dated_pending$concluded)`, and its tribunal is
treated as concluded on that date.

## The temporal hypergraph

The tribunals are built in the interval format. A case without a
conclusion date is active until `observation_end`, and the columns that are
constant within a case, such as the economic sector, are kept as attributes
of the hyperedge. The same construction on all ICSID tribunals, and on the
tribunals of the cases against other states, gives the systems the claims
against Argentina are compared with.

```{r build}
tribunals <- temporal_hypergraph(argentina, node = "arbitrator",
                                 hyperedge = "case", start = "constituted",
                                 end = "concluded",
                                 observation_end = as.Date("2023-06-15"))
summary(tribunals)
all_tribunals <- temporal_hypergraph(icsid_tribunals, node = "arbitrator",
                                     hyperedge = "case", start = "constituted",
                                     end = "concluded",
                                     observation_end = as.Date("2023-06-15"))
others <- subset(icsid_tribunals, respondent != "Argentine Republic")
other_tribunals <- temporal_hypergraph(others, node = "arbitrator",
                                       hyperedge = "case", start = "constituted",
                                       end = "concluded",
                                       observation_end = as.Date("2023-06-15"))
```

```{r build-values, include = FALSE}
mean_years <- summary(tribunals)$mean_duration / 365.25
```

A tribunal in the claims against Argentina sits for
`r num(mean_years, 1)` years on average. The cumulative snapshot at the end
of observation is the static aggregate of all tribunals. Four
representations of the aggregate differ in what they keep. The
multi-hypergraph (`mh`) keeps every tribunal, the binary hypergraph (`bh`)
keeps each distinct set of arbitrators once, and the clique expansions keep
(`mg`) or merge (`bg`) the repeated pairs of arbitrators.

```{r representations}
argentina_all <- hg_snapshot(tribunals, mode = "cumulative")
icsid_all <- hg_snapshot(all_tribunals, mode = "cumulative")
others_all <- hg_snapshot(other_tribunals, mode = "cumulative")
hg_representations(argentina_all)
```

```{r representations-values, include = FALSE}
reps <- hg_representations(argentina_all)
other_reps <- hg_representations(others_all)
rep_value <- function(r, col, x = reps) unlist(subset(x, representation == r, select = col), use.names = FALSE)
repeat_share <- (rep_value("mh", "n_edges") - rep_value("bh", "n_edges")) /
  rep_value("mh", "n_edges")
other_repeat_share <- (rep_value("mh", "n_edges", other_reps) -
                         rep_value("bh", "n_edges", other_reps)) /
  rep_value("mh", "n_edges", other_reps)
```

The clique expansion turns the `r rep_value("mh", "n_edges")` tribunals
into `r rep_value("mg", "n_edges")` ties between pairs of arbitrators, of
which `r rep_value("bg", "n_edges")` are distinct. Nothing in the graph
records that three ties came from one tribunal, so the repeated panels
examined below are invisible in it. The `r rep_value("mh", "n_edges")`
tribunals hold `r rep_value("bh", "n_edges")` distinct sets of arbitrators,
so `r pct(repeat_share)` of them repeat a panel that sat before, against
`r pct(other_repeat_share)` of the tribunals in the cases against other
states.

## Who decided the claims

The incidence view plots one row per arbitrator and one column per
tribunal, with a bar joining the three members of each tribunal. Rows are ordered by the number of tribunals, and columns by the date
of constitution. Colour and shape mark the economic sector.

```{r incidence, fig.width = 11, fig.height = 13}
plot(argentina_all, type = "incidence", color_by = "economic_sector",
     sort_by = "start", edge_labels = TRUE,
     legend_title = "economic sector")
```

```{r incidence-values, include = FALSE}
panels <- aggregate(arbitrator ~ case + constituted, data = argentina,
                    FUN = \(a) paste(sort(a), collapse = " | "))
repeated <- subset(panels, duplicated(arbitrator) |
                     duplicated(arbitrator, fromLast = TRUE))
pairs <- aggregate(case ~ arbitrator, data = repeated,
                   FUN = \(x) paste(sort(x), collapse = " and "))
same_day <- aggregate(constituted ~ arbitrator, data = repeated,
                      FUN = \(d) length(unique(d)) == 1L)
repeat_years <- sort(unique(format(repeated$constituted, "%Y")))
busiest <- subset(hg_get(argentina_all, what = "nodes"), degree >= 4)
busiest_seats <- subset(argentina, arbitrator %in% busiest$node)
busiest_early <- mean(busiest_seats$constituted < as.Date("2006-01-01"))
```

A tribunal that repeats a panel appears as a second column with dots in the
same three rows. The `r nrow(pairs)` repeated panels are the pairs
`r paste(pairs$case, collapse = ", ")`. All were constituted in
`r paste(repeat_years, collapse = " and ")`, and the two tribunals of
`r sum(same_day$constituted)` of the pairs on the same day. The
`r nrow(busiest)` arbitrators with four or more tribunals hold the top
rows, and `r pct(busiest_early)` of their seats are on tribunals constituted
before 2006.

The hyperdegree of an arbitrator is the number of tribunals on which the
arbitrator sat, and the degree in the clique expansion is the number of
distinct colleagues.

```{r degrees}
hg_get(argentina_all, what = "nodes", sort_by = "degree", top = 5)
tribunal_counts <- hg_measures(argentina_all, what = "distribution",
                               measure = "hyperdegree")
colleague_counts <- hg_measures(argentina_all, what = "distribution",
                                measure = "n_neighbors")
```

```{r degrees-values, include = FALSE}
one_tribunal <- 1 - subset(tribunal_counts, value == 2)$ccdf
top_arbitrator <- hg_get(argentina_all, what = "nodes", sort_by = "degree",
                         top = 1)
top_share <- function(h) {
  degrees <- hg_get(h, what = "nodes", sort_by = "degree")$degree
  sum(head(degrees, 10L)) / sum(degrees)
}
argentina_top <- top_share(argentina_all)
other_top <- top_share(others_all)
max_colleagues <- max(colleague_counts$value)
```

The figures plot the complementary cumulative distributions of the number
of tribunals and of the number of colleagues of an arbitrator.

```{r degrees-plot, fig.height = 4}
plot(tribunal_counts)
plot(colleague_counts)
```

Of the arbitrators, `r pct(one_tribunal)` sat on a single tribunal in these
cases, and `r top_arbitrator$node` sat on `r top_arbitrator$degree`. The
largest number of colleagues is `r max_colleagues`. The ten arbitrators with
the most tribunals, `r pct(10 / n_arbitrators)` of the arbitrators, hold
`r pct(argentina_top)` of the seats in the claims against Argentina; in the
cases against other states the ten busiest arbitrators hold
`r pct(other_top)`.

Degree assortativity asks whether arbitrators with many tribunals sit with
other arbitrators with many tribunals. From each tribunal a pair of
arbitrators is chosen at random, and the coefficient is the rank
correlation of their numbers of tribunals over all tribunals, a
generalised Spearman coefficient.

```{r assortativity}
hg_assortativity(argentina_all)
hg_assortativity(others_all)
```

```{r assortativity-values, include = FALSE}
assort_argentina <- hg_assortativity(argentina_all)$assortativity
assort_other <- hg_assortativity(others_all)$assortativity
```

The coefficient is `r num(assort_argentina)` for the claims against
Argentina and `r num(assort_other)` for the cases against other states. In both, the
busier arbitrators tend to share tribunals with each other, and the
tendency is stronger in the claims against Argentina.

## Repeated panels

A repeated collaboration is a pair or a set of three arbitrators who sit
together on more than one tribunal. The statistic `repeated_pairs` is the
number of pairs counted with their multiplicity minus the number of
distinct pairs, and `repeated_edges` is the number of tribunals whose set of
arbitrators sat before. Whether these counts exceed what the numbers of
tribunals of the arbitrators imply is tested against a null model. The swap
null keeps the number of tribunals of every arbitrator and the size of
every tribunal exactly and randomises the memberships by checkerboard
swaps. The assignment null is a looser alternative, in which the arbitrators are taken in decreasing order of hyperdegree and
assigned at random to tribunals with a free seat. Both are reported, each
with 999 draws.

```{r repeats}
repeats_swap <- hg_null_test(argentina_all,
                             statistic = c("repeated_pairs", "repeated_edges"),
                             method = "swap", n = 999, seed = 1)
repeats_swap
repeats_assignment <- hg_null_test(argentina_all,
                                   statistic = c("repeated_pairs", "repeated_edges"),
                                   method = "assignment", n = 999, seed = 1)
repeats_assignment
```

The same test on all ICSID tribunals, and on the tribunals of the cases
against other states, tells whether the claims against Argentina differ
from the system.

```{r repeats-icsid}
repeats_icsid <- hg_null_test(icsid_all,
                              statistic = c("repeated_pairs", "repeated_edges"),
                              method = "swap", n = 999, seed = 1)
repeats_icsid
repeats_other <- hg_null_test(others_all,
                              statistic = c("repeated_pairs", "repeated_edges"),
                              method = "swap", n = 999, seed = 1)
repeats_other
```

```{r repeats-values, include = FALSE}
test_value <- function(x, s, col) unlist(subset(x, statistic == s, select = col), use.names = FALSE)
```

Against the swap null, the claims against Argentina contain
`r test_value(repeats_swap, "repeated_pairs", "observed")` repeated pairs
(null range `r test_value(repeats_swap, "repeated_pairs", "null_lo")` to
`r test_value(repeats_swap, "repeated_pairs", "null_hi")`, z =
`r num(test_value(repeats_swap, "repeated_pairs", "z"), 1)`) and
`r test_value(repeats_swap, "repeated_edges", "observed")` repeated panels
(null range `r test_value(repeats_swap, "repeated_edges", "null_lo")` to
`r test_value(repeats_swap, "repeated_edges", "null_hi")`, z =
`r num(test_value(repeats_swap, "repeated_edges", "z"), 1)`, p =
`r num(test_value(repeats_swap, "repeated_edges", "p_value"), 3)`). The
assignment null gives z =
`r num(test_value(repeats_assignment, "repeated_pairs", "z"), 1)` for the
pairs and z =
`r num(test_value(repeats_assignment, "repeated_edges", "z"), 1)` for the
panels. Across all `r rep_value("mh", "n_edges", hg_representations(icsid_all))`
ICSID tribunals, the excess is modest: z =
`r num(test_value(repeats_icsid, "repeated_pairs", "z"), 1)` for the
`r test_value(repeats_icsid, "repeated_pairs", "observed")` repeated pairs
and z = `r num(test_value(repeats_icsid, "repeated_edges", "z"), 1)` for the
`r test_value(repeats_icsid, "repeated_edges", "observed")` repeated panels
(p = `r num(test_value(repeats_icsid, "repeated_edges", "p_value"), 2)`).
Without the claims against Argentina it disappears. In the cases against
other states, neither the
`r test_value(repeats_other, "repeated_pairs", "observed")` repeated pairs
(p = `r num(test_value(repeats_other, "repeated_pairs", "p_value"), 2)`) nor
the `r test_value(repeats_other, "repeated_edges", "observed")` repeated
panels (p = `r num(test_value(repeats_other, "repeated_edges", "p_value"), 2)`)
differ from the swap null. Under the null that keeps every margin exactly,
the repetition of arbitrators and panels found in ICSID as a whole is the
repetition in the claims against Argentina.

## Motifs

In a hypergraph whose hyperedges all have three nodes, four nodes can hold
up to four hyperedges. The motif Y has two of them, two tribunals that share
two arbitrators; T has three and O has all four. A motif count is compared
with its distribution under a configuration model that keeps the hyperdegree
of every node and the size of every hyperedge. The census of the aggregate
uses 1,000 draws.

```{r motifs}
motifs <- hg_motifs(argentina_all, n = 1000, seed = 1)
motifs
```

```{r motifs-values, include = FALSE}
motif_row <- function(x, m, col) unlist(subset(x, motif == m, select = col), use.names = FALSE)
```

```{r motifs-plot, fig.height = 4}
plot(motifs)
```

The aggregate contains `r motif_row(motifs, "Y", "count")` motifs Y against
a null mean of `r num(motif_row(motifs, "Y", "expected"), 1)` (z =
`r num(motif_row(motifs, "Y", "z"), 1)`, p =
`r num(motif_row(motifs, "Y", "p_value"), 3)`), and the motifs T and O do
not occur. The aggregate joins tribunals that never sat at the same time,
so the census is repeated on the snapshot of the first of January of each
year, which holds only the tribunals active together on that day.

```{r motifs-time}
years <- seq(as.Date("2003-01-01"), as.Date("2015-01-01"), by = "year")
yearly_motifs <- hg_motifs(tribunals, n = 300, seed = 1, at = years)
subset(yearly_motifs, motif == "Y",
       select = c(time, count, expected, z, p_value))
```

```{r motifs-time-values, include = FALSE}
yearly_y <- subset(yearly_motifs, motif == "Y")
max_y <- max(yearly_y$count)
min_p <- min(yearly_y$p_value)
```

No snapshot holds more than `r max_y` motifs Y, and the smallest p-value
of a snapshot is `r num(min_p, 2)`. The counts on a single day are too small
for the test to separate them from the null, and the excess is established
only for the aggregate.

## How the docket changed

Growth counts the active tribunals and arbitrators at each time, and the
columns ending in `_cumulative` count every tribunal begun by that time.
With `components = TRUE`, the number of connected components of the active
hypergraph, the share of its arbitrators in the largest component and the
diameter of that component are added. The grid is the first of January of
each year from 2002 to 2022.

```{r growth}
grid <- seq(as.Date("2002-01-01"), as.Date("2022-01-01"), by = "year")
docket <- hg_growth(tribunals, components = TRUE, at = grid)
```

```{r growth-plot, fig.height = 4}
plot(docket,
     columns = c("n_nodes", "n_edges", "n_nodes_cumulative",
                 "n_edges_cumulative"),
     facets = FALSE)
plot(docket, columns = c("n_components", "diameter"), facets = TRUE)
```

```{r growth-values, include = FALSE}
docket_year <- transform(docket, year = year_of(time),
                         per_tribunal = n_nodes / n_edges)
connected <- subset(docket_year, n_components == 1 & n_edges > 5)
widest <- head(subset(docket_year, diameter == max(diameter)), 1)
tightest <- head(subset(docket_year, per_tribunal == min(per_tribunal)), 1)
last_year <- tail(docket_year, 1)
```

On the first of January of `r paste(connected$year, collapse = " and ")`,
every active tribunal belonged to one connected component, with up to
`r max(connected$n_nodes)` arbitrators linked through shared seats. The two
most distant arbitrators of that component were `r widest$diameter` steps
apart in `r widest$year`, each step a tribunal on which two arbitrators sat
together. The component broke apart afterwards, and in `r last_year$year`
the `r last_year$n_edges` active tribunals formed
`r last_year$n_components` separate components. The number of active
arbitrators per active tribunal fell to `r num(tightest$per_tribunal)` in
`r tightest$year`, when the active tribunals shared many of their
arbitrators, and rose to `r num(last_year$per_tribunal)` in
`r last_year$year`, when no two active tribunals shared one.

The neighbourhood of a tribunal is the set of arbitrators who share a
tribunal with one of its members.

```{r neighbourhood}
neighbourhood <- hg_edges(tribunals, what = "summary", measure = "n_neighbors",
                          at = grid)
```

```{r neighbourhood-plot, fig.height = 4}
plot(neighbourhood, columns = c("mean", "q25", "median", "q75"),
     facets = FALSE)
```

```{r neighbourhood-values, include = FALSE}
largest_neighbourhood <- head(subset(neighbourhood, mean == max(mean)), 1)
```

The mean neighbourhood of an active tribunal peaks at
`r num(largest_neighbourhood$mean, 1)` arbitrators in
`r year_of(largest_neighbourhood$time)`.

## Which tribunals held the docket together

The s-betweenness of a tribunal is its betweenness centrality in the s-line
graph, in which two tribunals are adjacent when they share at least *s*
arbitrators. With *s* = 1, a tribunal of high betweenness lies on many of
the shortest chains of shared arbitrators between other tribunals.
Computed on the snapshot of each year, it shows which tribunal bridged the docket at
each time.

```{r bridges}
bridges <- hg_edge_centrality(tribunals, s = 1, measure = "betweenness",
                              at = grid, top = 1)
bridges
```

```{r bridges-values, include = FALSE}
bridging <- subset(bridges, value > 0)
first_quiet <- min(subset(bridges, value == 0 & time > as.Date("2010-01-01"))$time)
```

The bridge changes over time: `r length(unique(bridging$edge))` tribunals
hold the highest betweenness in at least one year. From
`r format(first_quiet, "%Y")` on, no active tribunal lies between two
others, because the active tribunals no longer share arbitrators.

On 1 June 2006, near the peak of the docket, the backbone is the ten
tribunals of highest betweenness in the snapshot of that day.

```{r backbone}
peak <- hg_snapshot(tribunals, at = as.Date("2006-06-01"))
backbone_cases <- hg_edge_centrality(peak, s = 1, measure = "betweenness",
                                     top = 10)
backbone <- hg_subset(peak, edges = backbone_cases)
```

```{r backbone-plot, fig.width = 10, fig.height = 7}
plot(backbone, color_by = "economic_sector", legend_title = "economic sector")
```

```{r backbone-values, include = FALSE}
hub <- hg_get(backbone, what = "nodes", sort_by = "degree", top = 1)
backbone_sectors <- length(unique(hg_get(backbone, what = "edge_data")$economic_sector))
```

On that day `r peak$n_hyperedges` tribunals were active. The ten tribunals
of the backbone span `r backbone_sectors` economic sectors and are joined
through a few arbitrators; `r hub$node` sits on `r hub$degree` of them.

The aggregate hypergraph gives a different backbone. Closeness computed on
all tribunals at once ranks tribunals as close to each other whether or
not they were ever active together.

```{r anachronism}
aggregate_cases <- hg_edge_centrality(argentina_all, s = 1,
                                      measure = "closeness", top = 10)
aggregate_cases
```

```{r anachronism-values, include = FALSE}
spans <- subset(hg_get(argentina_all, what = "edge_data"),
                edge %in% aggregate_cases$edge, select = c(edge, start, end))
spans <- transform(spans, end = ifelse(is.na(end), end_offset, end))
together <- outer(spans$start, spans$end, "<=") &
  outer(spans$end, spans$start, ">=")
apart_pairs <- sum(!together) / 2
all_pairs <- choose(nrow(spans), 2)
```

Of the `r all_pairs` pairs among these ten tribunals, `r apart_pairs` were
never active at the same time. A static centrality on the aggregate treats
the docket as if all of it had sat at once, which is the reason centrality
is computed here on snapshots.

## Communities of arbitrators

Hypergraph modularity measures the quality of a partition of the nodes into
communities, counting a hyperedge for a community when a majority of its
nodes belong to it. Iteratively reweighted modularity maximisation (IRMM)
finds a partition of high modularity, and Infomap partitions the
association graph by minimising the description length of a random walk on
it. Both are run from 20 seeds, and the partition reported is the
medoid, the run with the largest summed adjusted mutual information with
the other runs.

```{r communities}
irmm <- hg_communities(argentina_all, type = "irmm", seeds = 1:20,
                       n_runs = 20, max_iter = 300)
hg_modularity(argentina_all, irmm)
infomap <- hg_communities(argentina_all, seeds = 1:20, n_runs = 20)
hg_modularity(argentina_all, infomap)
hg_agreement(irmm, infomap, method = c("ari", "ami"))
```

```{r communities-values, include = FALSE}
irmm_sizes <- hg_get(irmm, what = "sizes")
irmm_ami <- hg_get(irmm, what = "ami")
irmm_modularity <- hg_modularity(argentina_all, irmm)
infomap_sizes <- hg_get(infomap, what = "sizes")
infomap_modularity <- hg_modularity(argentina_all, infomap)
infomap_ami <- hg_get(infomap, what = "ami")
partition_agreement <- hg_agreement(irmm, infomap, method = c("ari", "ami"))
```

The IRMM medoid has `r nrow(irmm_sizes)` communities of between
`r min(irmm_sizes$n_nodes)` and `r max(irmm_sizes$n_nodes)` arbitrators and
a modularity of `r num(irmm_modularity$modularity, 3)`, and its runs agree
with a median adjusted mutual information of `r num(median(irmm_ami$ami))`.
The Infomap medoid has `r nrow(infomap_sizes)` communities and a modularity
of `r num(infomap_modularity$modularity, 3)`, and its runs agree with a
median of `r num(median(infomap_ami$ami))`. The two medoids agree with an
adjusted Rand index of `r num(partition_agreement$ari)` and an adjusted
mutual information of `r num(partition_agreement$ami)`. The figure plots
the backbone of 1 June 2006 with each arbitrator coloured and shaped by its
IRMM community.

```{r communities-plot, fig.width = 10, fig.height = 7}
plot(backbone, node_groups = irmm)
```

## Argentina and the other cases

```{r comparison, echo = FALSE}
knitr::kable(data.frame(
  measure = c("tribunals", "arbitrators",
              "share of seats held by the ten busiest arbitrators",
              "share of tribunals that repeat a panel",
              "degree assortativity",
              "repeated panels, z against the swap null"),
  argentina = c(rep_value("mh", "n_edges"), rep_value("mh", "n_nodes"),
                pct(argentina_top), pct(repeat_share), num(assort_argentina),
                num(test_value(repeats_swap, "repeated_edges", "z"), 1)),
  other = c(rep_value("mh", "n_edges", other_reps),
            rep_value("mh", "n_nodes", other_reps),
            pct(other_top), pct(other_repeat_share), num(assort_other),
            num(test_value(repeats_other, "repeated_edges", "z"), 1))
), col.names = c("", "claims against Argentina", "cases against other states"))
```
