---
title: "Legal hypergraphs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Legal hypergraphs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE,
                      fig.width = 8, fig.height = 5, out.width = "100%",
                      dpi = 150)
library(hypergraphs)
has_igraph <- requireNamespace("igraph", quietly = TRUE)
comma <- function(x) format(x, big.mark = ",", trim = TRUE)
pct <- function(x) sprintf("%.0f%%", 100 * x)
```

A legal relation often binds more than two parties at once. An arbitral
tribunal binds its arbitrators for the duration of a case, and a citation
block, the set of earlier decisions cited together in one passage of a
judgment, binds those decisions to one another. Such relations are
hyperedges, and a collection of them observed over time is a temporal
hypergraph. Each hyperedge of a temporal hypergraph carries a time: an
interval, during which the hyperedge is active, or an instant, at which it
occurs. Coupette, Hartung and Katz (2024) model two legal systems in this
way and compare what the hypergraph and the graph built from the same data
show about them. This document reproduces their analyses on the released
data and extends them with hypergraph modularity. The methods are the
construction of temporal hypergraphs and their snapshots, descriptive
measures of growth, a null-model test of repeated collaboration, hyperedge
centrality, motifs, and communities.

## Data

The data were released by Coupette, Hartung and Katz (2024) under a CC
BY-NC 4.0 licence (Zenodo record 8081507) and ship with the package.
`icsid_tribunals` is a data frame with one row per seat on a tribunal of
the International Centre for Settlement of Investment Disputes (ICSID).
Each case has three seats. A row records the case, the seat, the
arbitrator, the dates on which the tribunal was constituted and the case
concluded, and attributes of the case such as its economic sector. A case
still pending at the end of observation has no conclusion date.

```{r data-icsid}
head(icsid_tribunals)
```

```{r data-icsid-values, include = FALSE}
n_cases <- length(unique(icsid_tribunals$case))
n_arbitrators <- length(unique(icsid_tribunals$arbitrator))
n_pending <- length(unique(subset(icsid_tribunals, !is_concluded)$case))
```

The data contain `r comma(n_cases)` cases heard by
`r comma(n_arbitrators)` arbitrators, of which `r n_pending` were pending on
15 June 2023, the end of observation.

The decisions of the German Federal Constitutional Court (GFCC) are held in
two data frames. `gfcc_decisions` has one row per decision with its date,
and `gfcc_citations` has one row per citation, with the citing decision,
the cited decision, the citation block, and the dates of the two decisions.

```{r data-gfcc}
head(gfcc_citations)
```

```{r data-gfcc-values, include = FALSE}
n_decisions <- nrow(gfcc_decisions)
n_citations <- nrow(gfcc_citations)
n_blocks <- length(unique(gfcc_citations$block))
first_year <- format(min(gfcc_decisions$date), "%Y")
last_year <- format(max(gfcc_decisions$date), "%Y")
```

The court issued `r comma(n_decisions)` decisions between
`r first_year` and `r last_year`, which contain
`r comma(n_citations)` citations in `r comma(n_blocks)` blocks.

## Temporal hypergraphs

A temporal hypergraph is built from membership data, one row per node and
hyperedge, with a column of times. Two formats of time are distinguished.
In the interval format, a hyperedge has a start and an end and is active on
the interval between them, which describes a tribunal that sits from its
constitution to the conclusion of its case. In the contact format, a
hyperedge has a single time and is an instantaneous event, which describes
a citation block that appears on the date of the citing decision. Dates
are converted to days since the first time in the data, and that origin
is reported with the object.

The tribunals are built in the interval format. The argument `node` names
the column of the arbitrators, `hyperedge` the column of the cases, and
`start` and `end` the columns of the dates. A case without a conclusion
date is active until `observation_end`. Columns that are constant within a
case, such as the economic sector, are kept as attributes of the hyperedge.

```{r icsid-build}
tribunals <- temporal_hypergraph(icsid_tribunals, node = "arbitrator",
                                 hyperedge = "case", start = "constituted",
                                 end = "concluded",
                                 observation_end = as.Date("2023-06-15"))
summary(tribunals)
```

Every tribunal has three arbitrators, so every hyperedge has size three,
and a tribunal sits for `r comma(round(summary(tribunals)$mean_duration))`
days on average.

The citation blocks are built in the contact format, with the cited
decision as the node, the block as the hyperedge and the date of the
citing decision as `time`. The data frame of decisions is passed as
`nodes`, so that a decision is a node from its own date whether or not it
is ever cited. The citing decision is constant within a block and becomes
an attribute of the hyperedge. With `sparse = TRUE` the incidence matrix
is stored as a sparse matrix.

```{r gfcc-build}
blocks <- temporal_hypergraph(gfcc_citations, node = "cited",
                              hyperedge = "block", time = "date_citing",
                              nodes = gfcc_decisions, sparse = TRUE)
summary(blocks)
```

```{r gfcc-build-values, include = FALSE}
block_summary <- summary(blocks)
```

The median block cites `r block_summary$median_edge_size` decision and the
mean block `r sprintf("%.2f", block_summary$mean_edge_size)`. These two
summaries are Table 1 of Coupette, Hartung and Katz (2024).

## Snapshots and representations

A snapshot is the static hypergraph of the hyperedges present at a time.
With `mode = "active"`, a snapshot holds the intervals that contain the
time; with `mode = "cumulative"`, it holds every hyperedge begun by that
time. A cumulative snapshot at the end of observation is the static
aggregate of the data. With `multiedges = FALSE`, hyperedges with the same
members are merged into one.

```{r snapshots}
tribunals_all <- hg_snapshot(tribunals, mode = "cumulative")
tribunals_active <- hg_snapshot(tribunals, at = as.Date("2023-06-15"),
                                mode = "active", multiedges = FALSE)
blocks_all <- hg_snapshot(blocks, mode = "cumulative")
```

The same data can be represented in four ways. The multi-hypergraph (`mh`)
keeps every hyperedge, the binary hypergraph (`bh`) keeps each distinct set
of members once, and the corresponding graphs keep (`mg`) or merge (`bg`)
repeated edges. For the tribunals, the graph is the clique expansion, in
which two arbitrators are joined when they sat on a tribunal together. The
degree of a node is its number of neighbours in a graph and its number of
hyperedges in a hypergraph.

```{r icsid-representations}
hg_representations(tribunals_all)
```

```{r icsid-representations-values, include = FALSE}
icsid_reps <- hg_representations(tribunals_all)
icsid_rep <- function(r, col) unlist(subset(icsid_reps, representation == r, select = col), use.names = FALSE)
```

An arbitrator has a median of `r icsid_rep("bg", "median_degree")`
colleagues and sits on a median of `r icsid_rep("mh", "median_degree")`
tribunals. The `r comma(icsid_rep("mh", "n_edges"))` tribunals hold
`r comma(icsid_rep("bh", "n_edges"))` distinct sets of arbitrators, so
`r icsid_rep("mh", "n_edges") - icsid_rep("bh", "n_edges")` tribunals
repeat a set that sat before.

For the citation blocks, the graph is the citation graph, in which the
citing decision is joined to each decision of the block. The argument
`graph = "citation"` selects it, and `edge_source` names the attribute that
holds the citing decision.

```{r gfcc-representations}
hg_representations(blocks_all, graph = "citation", edge_source = "citing")
```

```{r gfcc-representations-values, include = FALSE}
gfcc_reps <- hg_representations(blocks_all, graph = "citation",
                                 edge_source = "citing")
gfcc_rep <- function(r, col) unlist(subset(gfcc_reps, representation == r, select = col), use.names = FALSE)
```

A decision has a median of `r gfcc_rep("bg", "median_out_degree")`
outgoing citations in the binary citation graph and belongs to a median of
`r gfcc_rep("mh", "median_degree")` blocks in the multi-hypergraph. The
`r comma(gfcc_rep("mh", "n_edges"))` blocks hold
`r comma(gfcc_rep("bh", "n_edges"))` distinct sets of decisions, so a set
of decisions occurs in
`r sprintf("%.1f", gfcc_rep("mh", "n_edges") / gfcc_rep("bh", "n_edges"))`
blocks on average. These counts are
Table 2 of Coupette, Hartung and Katz (2024).

## One decision as a hypergraph

```{r headscarf-date, include = FALSE}
headscarf_date <- subset(gfcc_decisions, decision == "153-001")$date
```

The citations of a single decision form a hypergraph of its own, in which
each block is a hyperedge over the decisions it cites. With `where`, the
blocks whose `citing` attribute is decision 153-001, the decision of
`r format(headscarf_date, "%e %B %Y")` on the headscarf ban (Kopftuch III),
are kept.

```{r headscarf}
headscarf <- hg_subset(blocks_all, where = c(citing = "153-001"))
headscarf
```

```{r headscarf-values, include = FALSE}
headscarf_edges <- hg_get(headscarf)
n_alone <- sum(headscarf_edges$size == 1L)
headscarf_parts <- hg_measures(headscarf, what = "components")
largest_part <- head(headscarf_parts, 1)
```

The decision cites `r headscarf$n_nodes` decisions in
`r headscarf$n_hyperedges` blocks, and `r n_alone` of the blocks cite a
single decision. The figure plots each block of two or more decisions as a
hull around its members, coloured by its size, which is Figure 3 of
Coupette, Hartung and Katz (2024).

```{r headscarf-plot, fig.width = 7, fig.height = 7}
plot(headscarf, color_by = "size", labels = FALSE,
     legend_title = "block size")
```

The blocks form `r nrow(headscarf_parts)` connected components. The
largest joins `r largest_part$n_nodes` of the cited decisions through
`r largest_part$n_edges` overlapping blocks, which share decisions that
the judgment cites in several passages. The other blocks lie apart, and a
decision cited in a block of its own is a point outside every hull.

## Growth

The growth of a temporal hypergraph is the number of its nodes, hyperedges
and memberships at each time. With `mode = "cumulative"`, each count
includes everything that has appeared up to that time.

```{r gfcc-growth}
blocks_growth <- hg_growth(blocks, mode = "cumulative")
tail(blocks_growth, 3)
```

The figure plots the four counts against the date, Figure 4a of Coupette,
Hartung and Katz (2024).

```{r gfcc-growth-plot}
plot(blocks_growth,
     columns = c("n_nodes", "n_edges", "n_edges_distinct", "n_memberships"))
```

The number of decisions grows close to linearly over the seven decades,
and the numbers of blocks and memberships grow faster than linearly. At the
end of observation the `r comma(tail(blocks_growth, 1)$n_edges)` blocks
hold `r comma(tail(blocks_growth, 1)$n_edges_distinct)` distinct sets of
decisions, `r pct(tail(blocks_growth, 1)$n_edges_distinct / tail(blocks_growth, 1)$n_edges)`
of their number.

The size of a block is the number of decisions it cites. The distribution
of block sizes is computed for the cumulative hypergraph at five dates
given in `at`.

```{r gfcc-sizes}
census_dates <- as.Date(c("1960-12-31", "1975-12-31", "1990-12-31",
                          "2005-12-31", "2020-12-31"))
block_sizes <- hg_edges(blocks, what = "distribution", measure = "size",
                        at = census_dates, snapshot_mode = "cumulative")
```

The figure plots the complementary cumulative distribution of block size
at each date, Figure 4b of Coupette, Hartung and Katz (2024).

```{r gfcc-sizes-plot}
plot(block_sizes)
```

```{r gfcc-sizes-values, include = FALSE}
size_summary <- hg_edges(blocks, what = "summary", measure = "size",
                         at = census_dates, snapshot_mode = "cumulative")
```

The curves move to the right over time. The largest block cited
`r min(size_summary$max)` decisions by the end of 1960 and
`r max(size_summary$max)` by the end of 2020, and the mean size rose from
`r sprintf("%.2f", min(size_summary$mean))` to
`r sprintf("%.2f", max(size_summary$mean))`.

## Arbitrators and tribunals over time

The hyperdegree of an arbitrator is the number of tribunals on which the
arbitrator sat.

```{r icsid-degrees}
hg_get(tribunals_all, what = "nodes", sort_by = "degree", top = 5)
tribunal_counts <- hg_measures(tribunals_all, what = "distribution",
                               measure = "hyperdegree")
```

```{r icsid-degrees-values, include = FALSE}
share_two <- 1 - subset(tribunal_counts, value == 3)$ccdf
top_arbitrators <- hg_get(tribunals_all, what = "nodes", sort_by = "degree",
                          top = 2)
first_arbitrator <- head(top_arbitrators, 1)
second_arbitrator <- tail(top_arbitrators, 1)
```

The figure plots the complementary cumulative distribution of the
hyperdegree, Figure 5a of Coupette, Hartung and Katz (2024).

```{r icsid-degrees-plot, fig.height = 4}
plot(tribunal_counts)
```

The distribution is heavy-tailed. Of the arbitrators, `r pct(share_two)`
sat on one or two tribunals, and `r first_arbitrator$node` sat on
`r first_arbitrator$degree`, almost twice as many as the next
arbitrator, `r second_arbitrator$node`, with
`r second_arbitrator$degree`.

For a hypergraph in the interval format, growth counts the active
hyperedges at each time, and the columns ending in `_cumulative` count
every hyperedge begun by that time. With `components = TRUE`, the number of
connected components of the active hypergraph, the share of its nodes in
the largest component and the diameter of that component are added.

```{r icsid-growth}
tribunals_growth <- hg_growth(tribunals, components = TRUE)
tail(tribunals_growth, 3)
```

```{r icsid-growth-values, include = FALSE}
last_growth <- tail(tribunals_growth, 1)
recent <- subset(tribunals_growth,
                 time >= as.numeric(as.Date("2007-01-01") - as.Date("1974-10-07")))
```

The figure plots the active and cumulative counts of arbitrators and
tribunals, Figure 5b of Coupette, Hartung and Katz (2024).

```{r icsid-growth-plot, fig.height = 4}
plot(tribunals_growth,
     columns = c("n_nodes", "n_edges", "n_nodes_cumulative",
                 "n_edges_cumulative"),
     facets = FALSE)
```

At the end of observation, `r last_growth$n_edges` of the
`r last_growth$n_edges_cumulative` tribunals were active, with
`r last_growth$n_nodes` of the `r last_growth$n_nodes_cumulative`
arbitrators. The active counts stay close to zero until 2002 and rise
steeply after it. Since 2007 the largest component has held
between `r pct(min(recent$largest_component))` and
`r pct(max(recent$largest_component))` of the active arbitrators, and its
diameter has stayed between `r min(recent$diameter)` and
`r max(recent$diameter)`.

The neighbourhood of a tribunal is the set of arbitrators who share a
tribunal with one of its members. Its size is computed for every active
tribunal at every time, and `what = "summary"` returns its mean and
quartiles.

```{r icsid-neighbourhood}
neighbourhood <- hg_edges(tribunals, what = "summary", measure = "n_neighbors")
```

The figure plots these summaries over time, Figure 5c of Coupette,
Hartung and Katz (2024).

```{r icsid-neighbourhood-plot, fig.height = 4}
plot(neighbourhood, columns = c("mean", "q25", "median", "q75"),
     facets = FALSE)
```

```{r icsid-neighbourhood-values, include = FALSE}
last_neighbourhood <- tail(neighbourhood, 1)
```

The mean and the median stay close together, so the size of a
neighbourhood has a symmetric distribution, unlike the hyperdegree of an
arbitrator. At the end of observation the median tribunal had
`r last_neighbourhood$median` arbitrators in its neighbourhood.

## Repeated collaboration

A repeated collaboration is a pair or a set of three arbitrators who sit
together on more than one tribunal. The statistic `repeated_pairs` is the
number of pairs counted with their multiplicity minus the number of
distinct pairs, and `repeated_edges` is the number of tribunals whose set
of arbitrators sat before. A null model tells whether these counts exceed
what the number of tribunals of each arbitrator implies. In the null model
of Coupette, Hartung and Katz (2024), selected with
`method = "assignment"`, the arbitrators are taken in decreasing order of
hyperdegree, and each arbitrator is assigned to as many tribunals as the
arbitrator sat on, chosen at random among the tribunals with a free seat. The model keeps the
hyperdegree of every arbitrator and the size of every tribunal. Its draws
are not uniform over the hypergraphs with these margins, and the test
compares the observed count with 999 draws.

```{r icsid-repeats}
repeats <- hg_null_test(tribunals_all,
                        statistic = c("repeated_pairs", "repeated_edges"),
                        method = "assignment", n = 999, seed = 1)
repeats
```

```{r icsid-repeats-values, include = FALSE}
repeat_row <- function(s, col) unlist(subset(repeats, statistic == s, select = col), use.names = FALSE)
```

The tribunals contain `r repeat_row("repeated_pairs", "observed")`
repeated pairs, against a null range of
`r repeat_row("repeated_pairs", "null_lo")` to
`r repeat_row("repeated_pairs", "null_hi")`, and
`r repeat_row("repeated_edges", "observed")` repeated sets of three, against
a null range of `r repeat_row("repeated_edges", "null_lo")` to
`r repeat_row("repeated_edges", "null_hi")`. Both counts lie above every
null draw. Arbitrators who sat together once sit together again more often
than their numbers of tribunals explain.

## Hyperedge centrality

The s-line graph of a hypergraph has one vertex per hyperedge, and two
vertices are adjacent when their hyperedges share at least *s* nodes. The
s-betweenness of a hyperedge is its betweenness centrality in the s-line
graph, the share of shortest paths between other hyperedges that pass
through it, and its s-closeness is the inverse of its mean distance to the
other hyperedges. With *s* = 1, two tribunals are adjacent when they share
an arbitrator. The centralities are computed on the tribunals active at the
end of observation, with the normalisation of NetworkX that Coupette,
Hartung and Katz (2024) use.

```{r icsid-betweenness}
central_cases <- hg_edge_centrality(tribunals_active, s = 1,
                                    measure = "betweenness", top = 10)
central_cases
```

```{r icsid-closeness}
hg_edge_centrality(tribunals_active, s = 1, measure = "closeness", top = 10)
```

```{r icsid-centrality-values, include = FALSE}
close_cases <- hg_edge_centrality(tribunals_active, s = 1,
                                  measure = "closeness", top = 10)
n_shared <- length(intersect(central_cases$edge, close_cases$edge))
```

`r n_shared` of the ten tribunals with the highest betweenness are also
among the ten with the highest closeness. With `edges`, the ten tribunals
with the highest betweenness are kept, and the figure plots them coloured
by economic sector, Figure 6a of Coupette, Hartung and Katz (2024).

```{r icsid-central}
central_tribunals <- hg_subset(tribunals_active, edges = central_cases)
```

```{r icsid-central-plot, fig.width = 8, fig.height = 7}
plot(central_tribunals, color_by = "economic_sector",
     legend_title = "economic sector", label_size = 2.8)
```

```{r icsid-central-values, include = FALSE}
central_hub <- hg_get(central_tribunals, what = "nodes", sort_by = "degree",
                      top = 1)
```

The central tribunals are joined through a few arbitrators who sit on
several of them. `r central_hub$node` sits on
`r central_hub$degree` of the ten, and the tribunals span
`r length(unique(hg_get(central_tribunals, what = "edge_data")$economic_sector))`
economic sectors.

## Motifs

A motif is a small pattern of hyperedges over a fixed number of nodes. In a
hypergraph whose hyperedges all have three nodes, four nodes can hold up to
four hyperedges, one for each set of three. The motif Y has two of the four
hyperedges, T has three and O has all four. A motif count is compared with
its distribution under a configuration model that keeps the hyperdegree of
every node and the size of every hyperedge, sampled by repeated exchanges
of members between pairs of hyperedges (Lotito et al. 2023). The census is
computed on the aggregate of all tribunals, with 300 draws from the null
model.

```{r icsid-motifs}
motifs <- hg_motifs(tribunals_all, n = 300, seed = 1)
motifs
```

```{r icsid-motifs-values, include = FALSE}
motif_row <- function(m, col) unlist(subset(motifs, motif == m, select = col), use.names = FALSE)
```

The figure plots the null distribution of the count of Y with the observed
count, Figure 7c of Coupette, Hartung and Katz (2024).

```{r icsid-motifs-plot, fig.height = 4}
plot(motifs)
```

The tribunals contain `r motif_row("Y", "count")` motifs Y against a null
mean of `r round(motif_row("Y", "expected"))` (z =
`r sprintf("%.1f", motif_row("Y", "z"))`) and `r motif_row("T", "count")`
motifs T against a null mean of
`r sprintf("%.1f", motif_row("T", "expected"))`. The motif O does not
occur. Two tribunals that share two arbitrators form a Y, so the excess of
Y is the repeated collaboration of pairs seen in the null-model test.

## Communities of arbitrators

A community is a set of nodes that share more hyperedges with each other
than with the rest of the hypergraph. Hypergraph modularity measures the
quality of a partition of the nodes into communities (Kamiński et al. 2019).
Let hyperedge *e* have size \(d_e\) and weight \(w_e\), and let
\(W = \sum_e w_e\). For a partition, let \(c_e\) be the largest number of
nodes of *e* in one community. The hyperedge is owned by that community
when \(c_e > d_e/2\) and contributes \(w_e\,\omega(d_e, c_e)\) to it. The
linear weighting, \(\omega(d, c) = c/d\), is the default (Kamiński, Prałat
and Théberge 2020). The expected owned weight of a community *A* under a
null model that keeps the weighted degree of every node and the size of
every hyperedge is its degree tax,

\[
T_A = \sum_d W_d \sum_{c > d/2} \omega(d, c)\,
\binom{d}{c} p_A^{\,c} (1 - p_A)^{d-c},
\]

where \(W_d\) is the total weight of the hyperedges of size *d* and
\(p_A\) is the share of the weighted degree held by *A*. The modularity of
the partition is

\[
Q = \frac{1}{W}\Big(\sum_A E_A - \sum_A T_A\Big),
\qquad E_A = \sum_{e \text{ owned by } A} w_e\,\omega(d_e, c_e).
\]

A partition with a single community has \(Q = 0\). Iteratively reweighted
modularity maximisation (IRMM) finds a partition of high modularity (Kumar
et al. 2020). It maximises graph modularity on a weighted clique expansion
of the hypergraph with the Louvain method (Blondel et al. 2008), raises
the weight of the hyperedges that the partition keeps whole relative to
those it splits, and repeats until the weights settle. The Louvain step is
randomised, so IRMM is run from 20 seeds, and the partition reported is the
medoid, the run with the largest summed adjusted mutual information with
the other runs (Vinh, Epps and Bailey 2010). Modularity cannot resolve
communities below a size set by the total weight (Fortunato and Barthélemy
2007), and runs from different seeds reach different partitions of similar
modularity, so the agreement between runs is part of the result.

```{r icsid-irmm}
irmm <- hg_communities(tribunals_all, type = "irmm", seeds = 1:20,
                       n_runs = 20, max_iter = 300)
irmm
```

```{r icsid-irmm-values, include = FALSE}
irmm_sizes <- hg_get(irmm, what = "sizes")
irmm_runs <- hg_get(irmm, what = "runs")
irmm_ami <- hg_get(irmm, what = "ami")
```

The medoid has `r nrow(irmm_sizes)` communities of between
`r min(irmm_sizes$n_nodes)` and `r max(irmm_sizes$n_nodes)` arbitrators.
All `r nrow(irmm_runs)` runs converged, with between
`r min(irmm_runs$n_communities)` and `r max(irmm_runs$n_communities)`
communities, and two runs agree with a median adjusted mutual information
of `r sprintf("%.2f", median(irmm_ami$ami))`. The modularity of the medoid
is computed for the hypergraph.

```{r icsid-modularity}
irmm_modularity <- hg_modularity(tribunals_all, irmm)
irmm_modularity
```

The medoid owns a weighted share of
`r sprintf("%.2f", irmm_modularity$edge_contribution)` of the tribunals
against a degree tax of `r sprintf("%.2f", irmm_modularity$degree_tax)`,
for a modularity of `r sprintf("%.3f", irmm_modularity$modularity)`. The
runs reach modularities between
`r sprintf("%.3f", min(irmm_runs$modularity))` and
`r sprintf("%.3f", max(irmm_runs$modularity))`. The contribution of each
community shows where the score comes from.

```{r icsid-modularity-communities}
hg_modularity(tribunals_all, irmm, what = "communities")
```

```{r icsid-modularity-communities-values, include = FALSE}
by_community <- hg_modularity(tribunals_all, irmm, what = "communities")
small <- subset(by_community, n_nodes == 3L)
```

The largest communities contribute most of the score. The
`r nrow(small)` communities of three arbitrators are the small components
of the hypergraph, tribunals whose arbitrators never sat with anyone else.

The figure plots the ten central tribunals of the previous section with
each arbitrator coloured and shaped by its IRMM community.

```{r icsid-communities-plot, fig.width = 8, fig.height = 7}
plot(central_tribunals, node_groups = irmm, label_size = 2.8)
```

```{r icsid-communities-plot-values, include = FALSE}
central_partition <- merge(hg_get(central_tribunals, what = "memberships"),
                           hg_get(irmm), by = "node")
n_central_communities <- length(unique(central_partition$community))
n_central_arbitrators <- length(unique(central_partition$node))
communities_per_case <- aggregate(community ~ hyperedge, data = central_partition,
                                  FUN = \(x) length(unique(x)))
n_mixed <- sum(communities_per_case$community > 1L)
```

The `r n_central_arbitrators` arbitrators of the central tribunals belong
to `r n_central_communities` communities, and `r n_mixed` of the ten
tribunals join arbitrators of more than one community. A tribunal that is
central in the line graph connects parts of the hypergraph that modularity
separates.

Infomap partitions a graph by minimising the description length of a
random walk on it (Rosvall and Bergstrom 2008). The default method of
`hg_communities()` runs Infomap on the association graph of the
hypergraph, in which a hyperedge of size *d* adds \(1/(d-1)\) to the weight
of each pair of its members, following Coupette, Hartung and Katz (2024).

```{r icsid-infomap}
infomap <- hg_communities(tribunals_all, seeds = 1:20, n_runs = 20)
hg_modularity(tribunals_all, infomap)
```

```{r icsid-infomap-values, include = FALSE}
infomap_sizes <- hg_get(infomap, what = "sizes")
infomap_modularity <- hg_modularity(tribunals_all, infomap)
infomap_ami <- hg_get(infomap, what = "ami")
```

The Infomap medoid has `r nrow(infomap_sizes)` communities, and its
largest holds `r max(infomap_sizes$n_nodes)` arbitrators. It owns more of
the tribunals than the IRMM medoid, with an edge contribution of
`r sprintf("%.2f", infomap_modularity$edge_contribution)`, and pays a
larger degree tax, `r sprintf("%.2f", infomap_modularity$degree_tax)`,
for a modularity of `r sprintf("%.3f", infomap_modularity$modularity)`.
Two Infomap runs agree with a median adjusted mutual information of
`r sprintf("%.2f", median(infomap_ami$ami))`. The two partitions are
compared directly.

```{r icsid-agreement}
hg_agreement(irmm, infomap, method = c("ari", "ami"))
```

```{r icsid-agreement-values, include = FALSE}
partition_agreement <- hg_agreement(irmm, infomap, method = c("ari", "ami"))
```

The adjusted Rand index between the two medoids is
`r sprintf("%.2f", partition_agreement$ari)` and the adjusted mutual
information `r sprintf("%.2f", partition_agreement$ami)`. Infomap keeps
`r max(infomap_sizes$n_nodes)` arbitrators of the densely connected core in
one community, because a random walk remains in the core for long periods,
and IRMM divides the arbitrators among communities of at most
`r max(irmm_sizes$n_nodes)`. The two objectives give different partitions
of the same tribunals.

## Communities of decisions across representations

Coupette, Hartung and Katz (2024) partition the GFCC decisions in eight
representations and compare the partitions. Four are citation graphs,
binary (`bg`) or with multiplicities (`mg`), directed or undirected
(`bgu`, `mgu`). Four are association graphs of the hypergraph, binary
(`bh`) or with multiplicities (`mh`), with (`bhs`, `mhs`) or without self-association, the term that joins the citing decision to the decisions
of its block. The partitions use the backward citations, those whose
citing decision is later than the cited one.

```{r gfcc-backward}
backward_citations <- subset(gfcc_citations, date_citing > date_cited)
backward <- temporal_hypergraph(backward_citations, node = "cited",
                                hyperedge = "block", time = "date_citing",
                                nodes = gfcc_decisions, sparse = TRUE)
backward_all <- hg_snapshot(backward, mode = "cumulative")
```

Each representation is partitioned by Infomap from five seeds with five
trials each. The original analysis uses 50 seeds with 100 trials. The
citation graphs are selected with `method = "citation"`, the binary
representations with `duplicate_edges = "collapse"`, and self-association
with `self_association = TRUE`.

```{r gfcc-communities-graphs, eval = has_igraph}
communities_bg <- hg_communities(backward_all, n_runs = 5, trials = 5,
                                 seeds = 1:5, method = "citation",
                                 edge_source = "citing",
                                 duplicate_edges = "collapse", directed = TRUE)
communities_bgu <- hg_communities(backward_all, n_runs = 5, trials = 5,
                                  seeds = 1:5, method = "citation",
                                  edge_source = "citing",
                                  duplicate_edges = "collapse")
communities_mg <- hg_communities(backward_all, n_runs = 5, trials = 5,
                                 seeds = 1:5, method = "citation",
                                 edge_source = "citing", directed = TRUE)
communities_mgu <- hg_communities(backward_all, n_runs = 5, trials = 5,
                                  seeds = 1:5, method = "citation",
                                  edge_source = "citing")
```

```{r gfcc-communities-hypergraphs, eval = has_igraph}
communities_bh <- hg_communities(backward_all, n_runs = 5, trials = 5,
                                 seeds = 1:5, duplicate_edges = "collapse")
communities_bhs <- hg_communities(backward_all, n_runs = 5, trials = 5,
                                  seeds = 1:5, duplicate_edges = "collapse",
                                  self_association = TRUE,
                                  edge_source = "citing")
communities_mh <- hg_communities(backward_all, n_runs = 5, trials = 5,
                                 seeds = 1:5)
communities_mhs <- hg_communities(backward_all, n_runs = 5, trials = 5,
                                  seeds = 1:5, self_association = TRUE,
                                  edge_source = "citing")
```

The eight partitions are set side by side. With `hg`, each medoid is also
scored on the graph it was computed on. The quality measures are defined on
undirected graphs, so the two directed citation fits (`bg`, `mg`) get no
score and the comparison warns about them.

```{r gfcc-compare, eval = has_igraph}
comparison <- hg_compare_communities(
  bg = communities_bg, bgu = communities_bgu, mg = communities_mg,
  mgu = communities_mgu, bh = communities_bh, bhs = communities_bhs,
  mh = communities_mh, mhs = communities_mhs,
  hg = backward_all
)
comparison
```

```{r gfcc-compare-values, eval = has_igraph, include = FALSE}
compare_summary <- hg_get(comparison)
model_row <- function(m, col) unlist(subset(compare_summary, model == m, select = col), use.names = FALSE)
```

The association graphs without self-association leave
`r comma(model_row("bh", "n_singletons"))` (`bh`) and
`r comma(model_row("mh", "n_singletons"))` (`mh`) decisions as singletons,
the decisions that no later decision cites. With self-association a citing
decision is joined to the decisions it cites, and the number of singletons
falls to `r comma(model_row("bhs", "n_singletons"))` (`bhs`), close to the
`r comma(model_row("bg", "n_singletons"))` of the binary citation graph.
The figure plots
the distribution of community sizes in the eight partitions, Figure 8b of
Coupette, Hartung and Katz (2024).

```{r gfcc-compare-plot, eval = has_igraph, fig.height = 4}
plot(comparison)
```

The curves are close between sizes of about 3 and 30 and differ at both
ends. The partitions without self-association have the most singletons,
and the binary citation graphs have the largest communities, of
`r model_row("bg", "largest_size")` (`bg`) and
`r model_row("bgu", "largest_size")` (`bgu`) decisions, against
`r model_row("mh", "largest_size")` for `mh`. The similarity between
two partitions is measured by the adjusted mutual information and the
adjusted Rand index.

```{r gfcc-similarity, eval = has_igraph, fig.width = 6, fig.height = 5}
plot(comparison, what = "similarity")
```

```{r gfcc-similarity-values, eval = has_igraph, include = FALSE}
similarity <- hg_get(comparison, what = "similarity")
hyper <- c("bh", "bhs", "mh", "mhs")
within_hyper <- subset(similarity, model_a %in% hyper & model_b %in% hyper)
across <- subset(similarity, xor(model_a %in% hyper, model_b %in% hyper))
```

The figure shows the adjusted mutual information below the diagonal and
the adjusted Rand index above it, Figure 8c of Coupette, Hartung and Katz
(2024). Partitions of two hypergraph representations agree with a mean
adjusted mutual information of
`r sprintf("%.2f", mean(within_hyper$ami))`, and a partition of a
hypergraph representation agrees with a partition of a citation graph
with a mean of `r sprintf("%.2f", mean(across$ami))`. The quality of each
medoid is measured on its own graph by coverage, performance, modularity
and the largest conductance of a community.

```{r gfcc-quality, eval = has_igraph}
hg_get(comparison, what = "quality")
```

```{r gfcc-quality-values, eval = has_igraph, include = FALSE}
quality <- hg_get(comparison, what = "quality")
quality_hyper <- subset(quality, model %in% hyper)
quality_graph <- subset(quality, !model %in% hyper & !is.na(modularity))
```

The medoids of the hypergraph representations reach a graph modularity
between `r sprintf("%.2f", min(quality_hyper$modularity))` and
`r sprintf("%.2f", max(quality_hyper$modularity))` on their own graphs,
and those of the undirected citation graphs between
`r sprintf("%.2f", min(quality_graph$modularity))` and
`r sprintf("%.2f", max(quality_graph$modularity))`. Each score is computed
on a different graph, so the comparison describes how clearly each
representation divides into communities and does not rank the partitions
on a common scale.

## Interpretation

The hypergraph and the graph built from the same data describe the nodes
differently. An arbitrator sits on a median of
`r icsid_rep("mh", "median_degree")` tribunals but has a median of
`r icsid_rep("bg", "median_degree")` colleagues, and repeated sets of
colleagues, which the graph merges, exceed a null model that keeps every
arbitrator's number of tribunals. The excess of the motif Y is the same
repetition seen in groups of four arbitrators. The central tribunals and
the communities answer different questions. The central tribunals sit
between communities, and the partitions of the core of the hypergraph
depend on the objective, modularity or description length. For the court,
the partitions of the four hypergraph representations resemble each other
more than they resemble the partitions of the citation graphs.

## Limitations

The data end on 15 June 2023, and the tribunals pending on that date are
treated as active until then, so the active snapshot at the end of
observation includes cases of unknown length. The null model of the
repeated-collaboration test draws hypergraphs with the correct margins but
not uniformly among them. The motif census uses 300 draws and the GFCC
partitions five seeds with five trials, against 1,000 draws and 50 seeds
with 100 trials in the original analysis, so the tails of the null
distributions and the medoids are estimated with less precision. Hypergraph
modularity counts a hyperedge for a community only when a majority of its
nodes belong to that community, so for tribunals of three arbitrators a
tribunal split two to one counts as owned. Both community methods are
randomised, and a single run is not a finding.

## References

Blondel, V. D., Guillaume, J.-L., Lambiotte, R., & Lefebvre, E. (2008).
Fast unfolding of communities in large networks. *Journal of Statistical
Mechanics: Theory and Experiment*, 2008(10), P10008.
https://doi.org/10.1088/1742-5468/2008/10/P10008

Coupette, C., Hartung, D., & Katz, D. M. (2024). Legal hypergraphs.
*Philosophical Transactions of the Royal Society A*, 382(2270), 20230141.
https://doi.org/10.1098/rsta.2023.0141

Fortunato, S., & Barthélemy, M. (2007). Resolution limit in community
detection. *Proceedings of the National Academy of Sciences*, 104(1),
36–41. https://doi.org/10.1073/pnas.0605965104

Kamiński, B., Poulin, V., Prałat, P., Szufel, P., & Théberge, F. (2019).
Clustering via hypergraph modularity. *PLOS ONE*, 14(11), e0224307.
https://doi.org/10.1371/journal.pone.0224307

Kamiński, B., Prałat, P., & Théberge, F. (2020). Community detection
algorithm using hypergraph modularity. In *Complex Networks & Their
Applications IX*, Studies in Computational Intelligence 943, 152–163.
https://doi.org/10.1007/978-3-030-65347-7_13

Kumar, T., Vaidyanathan, S., Ananthapadmanabhan, H., Parthasarathy, S., &
Ravindran, B. (2020). Hypergraph clustering by iteratively reweighted
modularity maximization. *Applied Network Science*, 5, 52.
https://doi.org/10.1007/s41109-020-00300-3

Lotito, Q. F., Contisciani, M., De Bacco, C., Di Gaetano, L., Gallo, L.,
Montresor, A., Musciotto, F., Ruggeri, N., & Battiston, F. (2023).
Hypergraphx: a library for higher-order network analysis. *Journal of
Complex Networks*, 11(3), cnad019.

Rosvall, M., & Bergstrom, C. T. (2008). Maps of random walks on complex
networks reveal community structure. *Proceedings of the National Academy
of Sciences*, 105(4), 1118–1123. https://doi.org/10.1073/pnas.0706851105

Vinh, N. X., Epps, J., & Bailey, J. (2010). Information theoretic measures
for clusterings comparison: Variants, properties, normalization and
correction for chance. *Journal of Machine Learning Research*, 11,
2837–2854.
