---
title: "Constructions of a text hypergraph"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Constructions of a text hypergraph}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 8,
                      fig.height = 6, out.width = "100%")
library(hypergraphs)
join_and <- function(v) sub(", ([^,]*)$", " and \\1", toString(v))
ordinal <- function(k) {
  k <- as.integer(k)
  suffix <- if (k %% 100L %in% 11:13) "th" else
    c("th", "st", "nd", "rd", rep("th", 6L))[k %% 10L + 1L]
  sprintf("%d%s", k, suffix)
}
```

A text hypergraph relates the words and the documents of a corpus. Its
construction decides what a hyperedge is. A hyperedge can be a document,
which binds the words it contains, or a word, which binds the documents that
contain it. It can be a sentence, which binds the words used together in one
statement, or a short window of consecutive words, which binds words that
stand next to each other. It can also be a neighbourhood in a space of
sentence embeddings, which binds documents of similar meaning whatever their
words. Each construction relates different units, so the central words and
the groups of documents found in a corpus depend on it. `text_hypergraph()`
builds all of them with `construction = "bag"`, `"window"`, `"sentence"` or
`"knn"`. This document builds each construction first on three short
documents, where every hyperedge can be seen, and then on a corpus of
`r nrow(covid_abstracts)` abstracts, where the constructions give different
results.

## Three documents

The three documents below share some of their words. Stop words such as
"the" and "of" are removed with `stop_words_en()`.

```{r docs}
docs <- c(
  online   = "Students learn online. Teachers prepare online lessons.",
  assess   = "Teachers assess students. Online assessment needs feedback.",
  distance = "Distance learning needs feedback. Students value feedback."
)
stops <- stop_words_en()
```

### Bag of words

The bag construction relates each document to the words it contains, and it
ignores their order. With `nodes = "word"`, the words are the nodes and each
document is a hyperedge over its words. The orientation follows the setting
of Ding et al. (2020), in which a hyperedge holds the words of a text.

```{r bag-word}
bag_word <- text_hypergraph(docs, nodes = "word", stop_words = stops)
bag_word
```

```{r bag-word-values, include = FALSE}
toy_vocab <- hg_get(bag_word, what = "vocabulary")
in_all <- subset(toy_vocab, doc_freq == length(docs))$word
in_two <- subset(toy_vocab, doc_freq == 2)$word
```

The figure plots each document as a region around its words.

```{r bag-word-plot, fig.alt = "Three documents plotted as hyperedges over their words"}
plot(bag_word)
```

The three regions overlap where documents share words. `r join_and(in_all)`
lies in all three documents, and `r join_and(in_two)` lie in two. The other
words belong to one document each.

With `nodes = "doc"`, the default, the orientation reverses. The documents
are the nodes, and each word is a hyperedge over the documents that contain
it. This orientation suits the clustering and classification of documents
(Hayashi et al. 2020). Its incidence matrix is the transpose of the
incidence matrix above, so the two hypergraphs are duals of each other
(Berge 1989), and `dual_hypergraph()` turns one into the other.

```{r bag-doc}
bag_doc <- text_hypergraph(docs, stop_words = stops)
dual_hypergraph(bag_doc)
```

The dual of the document-oriented hypergraph has the `r nrow(toy_vocab)`
words as nodes and the `r length(docs)` documents as hyperedges, the same
hypergraph as `bag_word`.

The incidence weight of a word in a document is its count by default. With
`weight = "tfidf"`, the count is multiplied by the inverse document
frequency `log((1 + N) / (1 + df)) + 1`, where N is the number of documents
and df the number that contain the word (Manning et al. 2008). A word in
every document keeps its count, and a word in fewer documents gains weight.
The vocabulary table holds the count, the document frequency and the
inverse document frequency of each word.

```{r tfidf}
bag_tfidf <- text_hypergraph(docs, nodes = "word", weight = "tfidf",
                             stop_words = stops)
hg_get(bag_tfidf, what = "vocabulary")
```

```{r tfidf-values, include = FALSE}
tfidf_vocab <- hg_get(bag_tfidf, what = "vocabulary")
idf_all <- unique(round(subset(tfidf_vocab, doc_freq == 3)$idf, 2))
idf_one <- unique(round(subset(tfidf_vocab, doc_freq == 1)$idf, 2))
```

A word in all three documents has an inverse document frequency of
`r idf_all`, and a word in one document has `r idf_one`.

### Windows of words

The window construction keeps the order of the words. It slides a window of
`window` tokens over each document and makes a hyperedge of the distinct
words in each window (Ding et al. 2020). A window never crosses from one
document into the next, and windows with the same words form one hyperedge
whose weight is the number of such windows. With `window_mode = "sliding"`,
the default, the window moves one token at a time. With
`window_mode = "tumbling"`, it moves a whole window at a time, so the windows
do not overlap.

```{r window}
tumbling <- text_hypergraph(docs, construction = "window", window = 3,
                            window_mode = "tumbling", stop_words = stops)
tumbling
```

```{r window-values, include = FALSE}
sliding <- text_hypergraph(docs, construction = "window", window = 3,
                           stop_words = stops)
n_sliding <- length(unique(hg_get(sliding)$edge))
n_tumbling <- length(unique(hg_get(tumbling)$edge))
```

The figure plots each window as a region with its words and its count.

```{r window-plot, fig.alt = "Tumbling windows of three words plotted as hyperedges"}
plot(tumbling)
```

Each document has seven tokens after the stop words are removed, so it
gives two windows of three tokens and a last window of one. The last windows of the second and
third documents hold only `feedback`, so they form one hyperedge with a
count of 2. Words that stand far apart in a document share no window, so
`lessons` is linked to no other word. The sliding windows of the same size
give `r n_sliding` distinct hyperedges against `r n_tumbling` tumbling ones,
because every run of three consecutive words becomes a window.

### Sentences

The sentence construction makes a hyperedge of each sentence, the
construction of HyperGAT (Ding et al. 2020). A document is split at `.`,
`!`, `?` and `;`, and the weight of a word in a sentence is its count there.
Two words are related when they occur in the same sentence.

```{r sentence}
sentences <- text_hypergraph(docs, construction = "sentence",
                             stop_words = stops)
hg_get(sentences, what = "sentences")
```

The table has one row for each sentence, with its document, its position in
the document and its number of tokens.

```{r sentence-plot, fig.alt = "Six sentences plotted as hyperedges over their words"}
plot(sentences)
```

The six sentences split each document in two. `teachers` and `prepare`
share a sentence, and `teachers` and `feedback` share a document without
sharing a sentence. The bag construction relates the second pair and the
sentence construction does not.

### Neighbourhoods of meaning

The kNN construction uses no words. It places each document at a point in
the space of a sentence embedding, where documents with similar meaning lie
close together, and makes one hyperedge for each document from the document
and its `k` nearest neighbours by cosine similarity. Hypergraph neural
networks build hyperedges from feature space in this way (Feng et al. 2019).
The construction needs embeddings, which the corpus below provides.

## The corpus

`covid_abstracts` holds `r nrow(covid_abstracts)` abstracts of research on
education during COVID-19, and `covid_embeddings` their embeddings from the
`all-MiniLM-L6-v2` model, `r ncol(covid_embeddings)` numbers for each
abstract.

The vocabulary of a corpus has a long tail of rare words. `stop_words`
removes a list of words, `min_count` removes the words that occur fewer
times in the corpus, and `min_chars` removes words shorter than a number of
characters. `max_words` and `coverage` cap the vocabulary at a number of
words or at the most frequent words that cover a share of the tokens. Here
the stop words are those of `stop_words_en()` with words common to research
abstracts, `min_count = 3` keeps words that occur at least three times, and
`min_chars = 3` drops shorter fragments.

```{r corpus-vocabulary}
stops <- c(stop_words_en(), "using", "used", "use", "based", "results",
           "study", "research", "paper", "article", "findings", "data")
corpus_doc <- text_hypergraph(covid_abstracts, column = "abstract",
                              id = "doc", weight = "tfidf",
                              stop_words = stops, min_count = 3L,
                              min_chars = 3L)
head(hg_get(corpus_doc, what = "vocabulary"), 8)
```

```{r corpus-vocabulary-values, include = FALSE}
raw_corpus <- text_hypergraph(covid_abstracts, column = "abstract",
                              id = "doc")
n_raw <- nrow(hg_get(raw_corpus, what = "vocabulary"))
n_kept <- nrow(hg_get(corpus_doc, what = "vocabulary"))
```

The filters reduce the vocabulary from `r format(n_raw, big.mark = ",")`
words to `r format(n_kept, big.mark = ",")`. The same filters apply to every
token construction below, so the constructions differ only in what a
hyperedge is.

```{r corpus-constructions}
corpus_word <- text_hypergraph(covid_abstracts, column = "abstract",
                               id = "doc", nodes = "word", weight = "tfidf",
                               stop_words = stops, min_count = 3L,
                               min_chars = 3L)
corpus_window <- text_hypergraph(covid_abstracts, column = "abstract",
                                 id = "doc", construction = "window",
                                 window = 3, stop_words = stops,
                                 min_count = 3L, min_chars = 3L)
corpus_sentence <- text_hypergraph(covid_abstracts, column = "abstract",
                                   id = "doc", construction = "sentence",
                                   stop_words = stops, min_count = 3L,
                                   min_chars = 3L)
corpus_knn <- text_hypergraph(covid_abstracts, column = "abstract",
                              id = "doc", construction = "knn", k = 10,
                              embeddings = covid_embeddings)
```

```{r corpus-shape-values, include = FALSE}
shape <- function(x) {
  m <- hg_measures(x, what = "summary")
  setNames(m$value, m$measure)
}
s_doc <- shape(corpus_doc)
s_word <- shape(corpus_word)
s_window <- shape(corpus_window)
s_sentence <- shape(corpus_sentence)
s_knn <- shape(corpus_knn)
fmt <- function(v) format(round(v), big.mark = ",")
```

The constructions give hypergraphs of different shapes from the same text.
The document-oriented bag has `r fmt(s_doc[["n_nodes"]])` documents as nodes
and `r fmt(s_doc[["n_hyperedges"]])` words as hyperedges, each word in
`r round(s_doc[["avg_edge_size"]], 1)` documents on average. The
word-oriented bag is its dual, with `r fmt(s_word[["n_hyperedges"]])`
hyperedges of `r round(s_word[["avg_edge_size"]], 1)` words. The window
construction gives `r fmt(s_window[["n_hyperedges"]])` distinct windows of
up to three words, and the sentence construction
`r fmt(s_sentence[["n_hyperedges"]])` sentences of
`r round(s_sentence[["avg_edge_size"]], 1)` words on average. The kNN
construction has one hyperedge of `r round(s_knn[["avg_edge_size"]])`
documents for each abstract. In the bag, two words share a hyperedge when
they occur in the same abstract, which holds for
`r round(100 * s_word[["pairwise_participation"]])`% of the pairs of words.
In the sentence construction they must share a sentence, which holds for
`r round(100 * s_sentence[["pairwise_participation"]])`%, and in the window
construction they must stand within three words of each other, which holds
for `r round(100 * s_window[["pairwise_participation"]], 1)`%.

## Central words under three constructions

The bag, window and sentence constructions have the words as nodes. The
clique-motif eigenvector centrality of a word is its eigenvector centrality
in the clique expansion of the hypergraph, in which two words are linked
with a weight that grows with the hyperedges they share (Benson 2019). With
`sort_by = "clique"` and `n = 10`, each table shows the ten most central
words.

```{r centrality-bag}
hg_centrality(corpus_word, type = "clique", sort_by = "clique", n = 10)
```

```{r centrality-window}
hg_centrality(corpus_window, type = "clique", sort_by = "clique", n = 10)
```

```{r centrality-sentence}
hg_centrality(corpus_sentence, type = "clique", sort_by = "clique", n = 10)
```

```{r centrality-values, include = FALSE}
top_of <- function(x) {
  hg_centrality(x, type = "clique", sort_by = "clique", n = 10)$node
}
top_bag <- top_of(corpus_word)
top_window <- top_of(corpus_window)
top_sentence <- top_of(corpus_sentence)
shared_all <- Reduce(intersect, list(top_bag, top_window, top_sentence))
only_window <- setdiff(top_window, union(top_bag, top_sentence))
only_bag <- setdiff(top_bag, union(top_window, top_sentence))
window_rank <- hg_centrality(corpus_window, type = "clique",
                             sort_by = "clique")
bag_rank <- hg_centrality(corpus_word, type = "clique", sort_by = "clique")
distance_window <- which(window_rank$node == "distance")
distance_bag <- which(bag_rank$node == "distance")
sentence_rank <- hg_centrality(corpus_sentence, type = "clique",
                               sort_by = "clique")
distance_sentence <- which(sentence_rank$node == "distance")
abstract_text <- tolower(covid_abstracts$abstract)
distance_next <- sub("distance[- ]+", "",
                     unlist(regmatches(abstract_text,
                                       gregexpr("distance[- ]+[a-z]+",
                                                abstract_text))))
n_phrase <- sum(distance_next %in% c("education", "learning"))
```

The three constructions share `r length(shared_all)` of their ten words,
`r join_and(shared_all)`. These words occur throughout the corpus, so every
construction places them at the centre. The constructions differ at the end
of the lists. Only the window construction ranks
`r join_and(only_window)` among its ten, and only the bag ranks
`r join_and(only_bag)`. `distance` is `r ordinal(distance_window)` in the
window ranking, `r ordinal(distance_sentence)` in the sentence ranking and
`r ordinal(distance_bag)` in the bag ranking. Of its
`r length(distance_next)` occurrences, `r n_phrase` are followed by
`education` or `learning`, and the window construction links `distance` to
these words at every occurrence. The bag links `distance` to every word of
the abstracts that contain it and treats the phrase like any other pair of
words. The window construction thus raises the words of frequent phrases,
and the sentence construction, whose hyperedges are wider than a window and
narrower than an abstract, places `distance` between the two.

## Groups of documents under two constructions

The bag and kNN constructions have the documents as nodes. `hg_cluster()`
with `type = "random_walk"` partitions the documents by spectral clustering
on the Laplacian of the random walk on the hypergraph (Hayashi et al. 2020),
here into `k = 4` groups, and `seed = 1` fixes the random starts of its
k-means step. `hg_topic_sizes()` counts the documents in each group.

```{r clusters}
bag_groups <- hg_cluster(corpus_doc, k = 4, type = "random_walk", seed = 1)
hg_topic_sizes(corpus_doc, bag_groups)
knn_groups <- hg_cluster(corpus_knn, k = 4, type = "random_walk", seed = 1)
hg_topic_sizes(corpus_knn, knn_groups)
```

```{r cluster-values, include = FALSE}
bag_sizes <- hg_topic_sizes(corpus_doc, bag_groups)
knn_sizes <- hg_topic_sizes(corpus_knn, knn_groups)
```

The bag groups hold between `r min(bag_sizes$n)` and `r max(bag_sizes$n)`
documents, and the kNN groups between `r min(knn_sizes$n)` and
`r max(knn_sizes$n)`. A kNN hyperedge holds the same number of documents for
every abstract, which spreads the documents evenly. A bag hyperedge holds
every document that uses a word, so common words bind many documents
together.

The kNN hypergraph holds no words, so the words of its groups are read from
the bag. `hg_keywords()` ranks the words of each group by their mass, the
summed tf-idf weight that the documents of the group place on the word. The
figure plots the eight words of largest mass in each group.

```{r knn-keywords, fig.width = 10, fig.height = 9, fig.alt = "The eight words with the largest tf-idf mass in each kNN group"}
knn_keywords <- hg_keywords(corpus_doc, knn_groups, n = 8)
plot(knn_keywords)
```

```{r knn-keywords-values, include = FALSE}
lead_words <- vapply(split(knn_keywords$word, knn_keywords$cluster),
                     \(w) toString(head(w, 4)), character(1L))
```

The groups lead with
`r paste(sprintf("%s (%s)", names(lead_words), lead_words), collapse = "; ")`.
Each group is a theme of research on education in the pandemic, and the
kNN construction finds the themes from the meaning of the abstracts alone.

The words of the bag groups come from the same table.

```{r bag-keywords}
hg_keywords(corpus_doc, bag_groups, n = 8)
```

`hg_agreement()` with `what = "table"` cross-tabulates the two partitions,
one row for each pair of a kNN group and a bag group with the number of
documents they share. Without `what`, it gives the summary. `aligned`
counts the documents that fall in the bag group holding most of their kNN
group, `agreement` is their share, and `ari` is the adjusted Rand index,
which is 1 for identical partitions and near 0 for unrelated ones.

```{r agreement}
hg_agreement(knn_groups, bag_groups, what = "table")
hg_agreement(knn_groups, bag_groups)
```

```{r agreement-values, include = FALSE}
agree <- hg_agreement(knn_groups, bag_groups)
cross <- hg_agreement(knn_groups, bag_groups, what = "table")
best <- merge(aggregate(n ~ label_x, data = cross, FUN = max), cross)
group_size <- aggregate(n ~ label_x, data = cross, FUN = sum)
names(group_size) <- c("label_x", "size")
best <- merge(best, group_size)
best$share <- best$n / best$size
best <- sort_by(best, ~ share, decreasing = TRUE)
bag_lead <- hg_keywords(corpus_doc, bag_groups, n = 3)
bag_words <- aggregate(word ~ cluster, data = bag_lead, FUN = toString)
knn_lead <- hg_keywords(corpus_doc, knn_groups, n = 3)
knn_words <- aggregate(word ~ cluster, data = knn_lead, FUN = toString)
best <- merge(best, setNames(knn_words, c("label_x", "knn_words")))
best <- merge(best, setNames(bag_words, c("label_y", "bag_words")))
best <- sort_by(best, ~ share, decreasing = TRUE)
matched <- head(best, 2)
cross_words <- merge(cross, setNames(bag_words, c("label_y", "bag_words")))
cross_words <- merge(cross_words, setNames(knn_words, c("label_x", "knn_words")))
clinical_knn <- subset(cross_words, grepl("clinical", knn_words))
clinical_own <- subset(clinical_knn, grepl("clinical", bag_words))
clinical_top <- subset(clinical_knn, n == max(n))
clinical_size <- sum(clinical_knn$n)
clinical_bag <- subset(hg_topic_sizes(corpus_doc, bag_groups),
                       topic == clinical_own$label_y)
```

The two partitions find the same themes and draw their boundaries
differently. `r agree$aligned` of the `r agree$n` documents are aligned, and
the adjusted Rand index is `r round(agree$ari, 2)`. The themes of school and
of online learning agree. The kNN group on
`r matched$knn_words[1]` has `r matched$n[1]` of its `r matched$size[1]`
documents in the bag group on `r matched$bag_words[1]`, and the kNN group on
`r matched$knn_words[2]` has `r matched$n[2]` of its `r matched$size[2]` in
the bag group on `r matched$bag_words[2]`. The theme of clinical teaching
differs. The kNN group on `r clinical_own$knn_words` keeps
`r clinical_own$n` of its `r clinical_size` documents in the bag group on
`r clinical_own$bag_words`, which holds only `r clinical_bag$n` documents,
and places `r clinical_top$n` in the bag group on
`r clinical_top$bag_words`. The bag forms a small group from the
abstracts whose vocabulary is clinical and dental, and it places most of the
other abstracts of the kNN group with the abstracts on online learning,
whose words they share. The kNN construction keeps these abstracts in one group
because their embeddings lie close together.

## Choice of construction

The construction follows from the relation that the analysis is about. The
bag relates documents through shared words. Its document orientation suits
the clustering and classification of documents, and its word orientation
the centrality of words across documents. The window construction relates
words that stand next to each other, which suits phrases and collocations.
Its number of distinct windows grows with the size of the corpus, which
`min_count` and the other filters keep in check. The sentence construction
relates words used in one statement, a narrower relation than the document
and a wider one than the window. The kNN construction relates documents by
meaning and uses no words, so its results depend on the encoder that
produced the embeddings, and a result that matters is repeated with a second
encoder.

## References

Benson, A. R. (2019). Three hypergraph eigenvector centralities. *SIAM
Journal on Mathematics of Data Science*, 1(2), 293-312.

Berge, C. (1989). *Hypergraphs: Combinatorics of Finite Sets*.
North-Holland.

Ding, K., Wang, J., Li, J., Li, D., & Liu, H. (2020). Be more with less:
Hypergraph attention networks for inductive text classification.
*Proceedings of EMNLP 2020*, 4927-4936.
https://doi.org/10.18653/v1/2020.emnlp-main.399

Feng, Y., You, H., Zhang, Z., Ji, R., & Gao, Y. (2019). Hypergraph neural
networks. *Proceedings of the AAAI Conference on Artificial Intelligence*,
33(01), 3558-3565. https://doi.org/10.1609/aaai.v33i01.33013558

Hayashi, K., Aksoy, S. G., Park, C. H., & Park, H. (2020). Hypergraph random
walks, Laplacians, and clustering. *Proceedings of CIKM 2020*, 495-504.
https://doi.org/10.1145/3340531.3412034

Manning, C. D., Raghavan, P., & Schütze, H. (2008). *Introduction to
Information Retrieval*. Cambridge University Press.
